%% start of file `template.tex'.
%% Copyright 2006-2012 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}

% moderncv themes
\moderncvstyle{classic}                        % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                          % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}    % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                  % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                         % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}           % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}      % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\firstname{Victor}
\familyname{Dodon}
\address{Splaiul Independentei St, P16, room 042, Bucharest,
Romania}{060029}    % optional, remove the line if not wanted
\mobile{+40 742 324 309}                     % optional, remove the line if not wanted
\email{dodonvictor@gmail.com}                          % optional, remove the line if not wanted

\definecolor{linkcolour}{rgb}{0,0,0.6}
\usepackage{hyperref}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\begin{document}
% recipient data
\recipient{Google Recruitment team}{Google Inc.\\1600 Amphitheatre
Parkway\\Mountain View, CA 94043 USA}
\date{October 21, 2012}
\opening{Dear Hiring Manager,}
\closing{Sincerely,}
\makelettertitle

I hope you will consider me for the position of Software Engineering
Intern at Google during the summer of 2013.

I am very excited about the possibility to work at such a big and
important IT company as Google. I'm really impressed about the excellent products
and the filosophy of this company and I would love the opportunity to
use my potential to contribute to your great but complex work.

I think I'm suitable for this position, after reading on the job
description, because, as you can see from my resume, I have excelent knowlegde
of C and C++ languages, I have a very good knowlegde of UNIX/Linux environment 
and I'm familiar with TCP/IP and network programming.

Additionally, I am a tireless person dedicated to the computer science
and keen for quality. I am a fast learner and I love challenges.

I think my skills and my type are an excellent match for what you are
seeking and I am excited about the chance to work with you.

Thank you for your consideration.

\makeletterclosing
\end{document}

%% end of file `template.tex'.

